PANCHANGE_data_preprocessing

### 2020-09-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed OCI-R retro and baseline scoring by changing to using the numeric variables.

```{r ocir prepan sum score if missigng items set to NA - all items}
if(GLAD == TRUE | EDGI == TRUE) {
prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
  mutate(
    ocir.sum_score_prepan =
      if_else(condition = na_per_person_ocir_prepan > 0,
              true = NA_real_,
              false = ocir.sum_score_prepan_raw,
              missing = NA_real_
      )
  )

@@

# Create vector with items that are included in total score
ocir.items_retro = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
  "ocir.arranged_things_change_upset_retro",
  "ocir.repeat_feel_numbers_retro",
  "ocir.clean_simply_wash_feel_retro",
  "ocir.mind_upset_unpleasant_thoughts_retro",
  "ocir.afraid_avoid_throwing_things_retro",
  "ocir.light_switches_water_taps_retro",
  "ocir.arranged_things_retro",
  "ocir.good_feel_bad_numbers_retro",
  "ocir.hands_longer_wash_retro",
  "ocir.saved_things_retro",
  "ocir.frequently_difficulty_rid_nasty_retro",
  "ocir.i_check_things_more_often_than_necessary_retro",
  "ocir.arranged_properly_objects_upset_retro",
  "ocir.feel_compelled_count_things_retro",
  "ocir.strangers_touch_touched_difficult_retro",
  "ocir.control_difficult_find_thoughts_retro",
  "ocir.i_collect_things_i_dont_need_retro"
)

@@

# Create vector with items that are included in total score
ocir.items_base = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
  "ocir.arranged_things_change_upset_base",
  "ocir.repeat_feel_numbers_base",
  "ocir.clean_simply_wash_feel_base",
  "ocir.mind_upset_unpleasant_thoughts_base",
  "ocir.afraid_avoid_throwing_things_base",
  "ocir.light_switches_water_taps_base",
  "ocir.arranged_things_base",
  "ocir.good_feel_bad_numbers_base",
  "ocir.hands_longer_wash_base",
  "ocir.saved_things_base",
  "ocir.frequently_difficulty_rid_nasty_base",
  "ocir.i_check_things_more_often_than_necessary_base",
  "ocir.arranged_properly_objects_upset_base",
  "ocir.feel_compelled_count_things_base",
  "ocir.strangers_touch_touched_difficult_base",
  "ocir.control_difficult_find_thoughts_base",
  "ocir.i_collect_things_i_dont_need_base"
)

@@

nbr.als.raw.id <- nbr.als.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         alsfrs.limb_weakness_noticed_past,
         alsfrs.normal,
         alsfrs.slow_or_sloppy_all_words_are_legible,
         alsfrs.not_all_words_are_legible,
         alsfrs.able_to_grip_pen,
         alsfrs.unable_to_grip_pen,
         alsfrs.have_you_noticed_any_difficulty_walking,
         alsfrs.do_you_have_any_difficulty_climbing_stairs
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.als.raw.id <- ramp.als.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         alsfrs.limb_weakness_noticed_past = alsfrs.limb_weakness_past_month,
         alsfrs.normal,
         alsfrs.slow_or_sloppy_all_words_are_legible,
         alsfrs.not_all_words_are_legible,
         alsfrs.able_to_grip_pen,
         alsfrs.unable_to_grip_pen,
         alsfrs.have_you_noticed_any_difficulty_walking,
         alsfrs.do_you_have_any_difficulty_climbing_stairs
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

glad.ess.raw.id <- glad.ess.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none   
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

edgi.ess.raw.id <- edgi.ess.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour = ess.break_passenger_hour_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.ess.raw.id <- nbr.ess.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.ess.raw.id <- ramp.ess.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past = ess.felt_excessively_sleepy_day,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour = ess.break_hour_passenger_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic#,
#         ess.insomnia, # questions are not asked in RAMP
#         ess.narcolepsy,
#         ess.rem_sleep_behaviour_disorder,
#         ess.restless_legs_syndrome,
#         ess.sleep_apnea,
#         ess.sleep_terrors,
#         ess.sleepwalking,
#         ess.other,
#         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
    add_column(
    ess.insomnia = NA_character_,
    ess.narcolepsy = NA_character_,
    ess.rem_sleep_behaviour_disorder = NA_character_,
    ess.restless_legs_syndrome = NA_character_,
    ess.sleep_apnea = NA_character_,
    ess.sleep_terrors = NA_character_,
    ess.sleepwalking = NA_character_,
    ess.other = NA_character_,
    ess.none = NA_character_,
    ess.insomnia_numeric = NA_real_,
    ess.narcolepsy_numeric = NA_real_,
    ess.rem_sleep_behaviour_disorder_numeric = NA_real_,
    ess.restless_legs_syndrome_numeric = NA_real_,
    ess.sleep_apnea_numeric = NA_real_,
    ess.sleep_terrors_numeric = NA_real_,
    ess.sleepwalking_numeric = NA_real_,
    ess.other_numeric = NA_real_,
    ess.none_numeric = NA_real_
    ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

glad.midas.raw.id <- glad.midas.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         midas.headaches_suffered_past_month,
         midas.days_past_month_miss_work_school = midas.past_month_days,
         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
         midas.days_past_month_miss_housework = midas.past_month_days.2,
         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
         midas.days_past_month_miss_social_activities = midas.past_month_days.4
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr midas summary labels}
if(NBR == TRUE) {
summarytools::dfSummary(
  nbr.midas.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

@@

```{r ramp midas summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  ramp.midas.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

@@

```{r ramp tinnitus summary labels}
if(NBR == TRUE) {
summarytools::dfSummary(
  nbr.tinnitus.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

>>>>

```{r ocir prepan sum score if missing items set to NA - all items}
if(GLAD == TRUE | EDGI == TRUE) {
prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
  mutate(
    ocir.sum_score_prepan =
      if_else(condition = na_per_person_ocir_prepan > 0,
              true = NA_real_,
              false = ocir.sum_score_prepan_raw,
              missing = NA_real_
      )
  )

@@

# Create vector with items that are included in total score
ocir.items_retro = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro_numeric",
  "ocir.arranged_things_change_upset_retro_numeric",
  "ocir.repeat_feel_numbers_retro_numeric",
  "ocir.clean_simply_wash_feel_retro_numeric",
  "ocir.mind_upset_unpleasant_thoughts_retro_numeric",
  "ocir.afraid_avoid_throwing_things_retro_numeric",
  "ocir.light_switches_water_taps_retro_numeric",
  "ocir.arranged_things_retro_numeric",
  "ocir.good_feel_bad_numbers_retro_numeric",
  "ocir.hands_longer_wash_retro_numeric",
  "ocir.saved_things_retro_numeric",
  "ocir.frequently_difficulty_rid_nasty_retro_numeric",
  "ocir.i_check_things_more_often_than_necessary_retro_numeric",
  "ocir.arranged_properly_objects_upset_retro_numeric",
  "ocir.feel_compelled_count_things_retro_numeric",
  "ocir.strangers_touch_touched_difficult_retro_numeric",
  "ocir.control_difficult_find_thoughts_retro_numeric",
  "ocir.i_collect_things_i_dont_need_retro_numeric"
)

@@

# Create vector with items that are included in total score
ocir.items_base = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base_numeric",
  "ocir.arranged_things_change_upset_base_numeric",
  "ocir.repeat_feel_numbers_base_numeric",
  "ocir.clean_simply_wash_feel_base_numeric",
  "ocir.mind_upset_unpleasant_thoughts_base_numeric",
  "ocir.afraid_avoid_throwing_things_base_numeric",
  "ocir.light_switches_water_taps_base_numeric",
  "ocir.arranged_things_base_numeric",
  "ocir.good_feel_bad_numbers_base_numeric",
  "ocir.hands_longer_wash_base_numeric",
  "ocir.saved_things_base_numeric",
  "ocir.frequently_difficulty_rid_nasty_base_numeric",
  "ocir.i_check_things_more_often_than_necessary_base_numeric",
  "ocir.arranged_properly_objects_upset_base_numeric",
  "ocir.feel_compelled_count_things_base_numeric",
  "ocir.strangers_touch_touched_difficult_base_numeric",
  "ocir.control_difficult_find_thoughts_base_numeric",
  "ocir.i_collect_things_i_dont_need_base_numeric"
)

@@

nbr.als.raw.id <- nbr.als.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         alsfrs.limb_weakness_noticed_past,
         alsfrs.normal,
         alsfrs.slow_or_sloppy_all_words_are_legible,
         alsfrs.not_all_words_are_legible,
         alsfrs.able_to_grip_pen,
         alsfrs.unable_to_grip_pen,
         alsfrs.have_you_noticed_any_difficulty_walking,
         alsfrs.do_you_have_any_difficulty_climbing_stairs
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.als.raw.id <- ramp.als.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         alsfrs.limb_weakness_noticed_past,
         alsfrs.normal,
         alsfrs.slow_or_sloppy_all_words_are_legible,
         alsfrs.not_all_words_are_legible,
         alsfrs.able_to_grip_pen,
         alsfrs.unable_to_grip_pen,
         alsfrs.have_you_noticed_any_difficulty_walking,
         alsfrs.do_you_have_any_difficulty_climbing_stairs
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

glad.ess.raw.id <- glad.ess.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past= ess.day_past_month_felt,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_hour_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none   
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

edgi.ess.raw.id <- edgi.ess.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_hour_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.ess.raw.id <- nbr.ess.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_hour_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.ess.raw.id <- ramp.ess.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_hour_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic,
         ess.insomnia,
         ess.narcolepsy,
         ess.rem_sleep_behaviour_disorder,
         ess.restless_legs_syndrome,
         ess.sleep_apnea,
         ess.sleep_terrors,
         ess.sleepwalking,
         ess.other,
         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

glad.midas.raw.id <- glad.midas.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         midas.headaches_suffered_past_month,
         midas.days_past_month_miss_work_school = midas.days_past_month,
         midas.days_past_month_work_school_half_productivity = midas.days_past_month.1,
         midas.days_past_month_miss_housework = midas.days_past_month.2,
         midas.days_past_month_housework_half_productivity = midas.days_past_month.3,
         midas.days_past_month_miss_social_activities = midas.days_past_month.4
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

@@

@@
